---
title: "Simple document"
output:
  html_document:
    toc: true
    toc_float: true
    code_folding: hide
---

```{r}
library(tidyverse)
```


I'm an R Markdown document! 

# Section 1

Here's a **code chunk** that samples from 
a _normal distribution_:

```{r}
samp = rnorm(100)
length(samp)
```

# Section 2

I can take the mean of the sample, too!
The mean is `r mean(samp)`.

# Section 3

This is going to make a scatter plot a scatter plot using `ggplot`.

```{r chunk_scatterplot}
plot_df = 
  tibble(
    x = rnorm(n=1000),
    y = 1 + 2 * x^2 + rnorm(n=1000) 
  )

ggplot(plot_df, aes(x=x, y=y)) + geom_point()
```

# section 4

```{r, echo=FALSE}
plot_df = 
  tibble(
    x = rnorm(n=1000),
    y = 1 + 2 * x^2 + rnorm(n=1000) 
  )
ggplot(plot_df, aes(x=x, y=y)) + geom_point()
```

# section 5

```{r, eval=FALSE}
plot_df = 
  tibble(
    x = rnorm(n=1000),
    y = 1 + 2 * x^2 + rnorm(n=1000) 
  )
ggplot(plot_df, aes(x=x, y=y)) + geom_point()
```


# plot for learning assessment

```{r assessment}
df = 
  tibble(
    var_numeric = rnorm(n=500, mean=1),
    logical = var_numeric > 0,
    absolute = abs(var_numeric),
    )
ggplot(df, aes(x=absolute)) + geom_histogram()
```

Text formatting 
------------------------------------------------------------

*italic*  or  _italic_
**bold**  or  __bold__
`code`
superscript^2^ and subscript~2~


Headings
------------------------------------------------------------

# 1st Level Header

## 2nd Level Header

### 3rd Level Header


Lists
------------------------------------------------------------

*   Bulleted list item 1

*   Item 2

    * Item 2a

    * Item 2b

1.  Numbered list item 1

1.  Item 2. The numbers are incremented automatically in the output.


Tables 
------------------------------------------------------------

First Header  | Second Header
------------- | -------------
Content Cell  | Content Cell
Content Cell  | Content Cell

